\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2016-07-10 papers/jss-finalising/v71i02.tex
finalising: content of emailed zip file
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@952 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\author{Dirk Eddelbuettel\\Debian Project \And 
        Murray Stokely\\Google, Inc. \And
        Jeroen Ooms\\University of California,\\Los Angeles}
\Plainauthor{Dirk Eddelbuettel, Murray Stokely, Jeroen Ooms}

@@

  Murray Stokely\\
  Google, Inc.\\
  1600 Amphitheatre Parkway\\
  Mountain View, CA, United States of America\\
  E-mail: \email{mstokely@google.com}\\
  URL: \url{http://www.stokely.org/}\\

@@

  Data set & \code{object.size} & \multicolumn{2}{c}{\proglang{R} serialization} &
  \multicolumn{2}{c}{\pkg{RProtoBuf} serialization} \\
  & & default & gzipped & default & gzipped \\
  \hline
 \code{crimtab} & 7,936 & 4,641 (41.5\%) & 713 (91.0\%) & 1,655 (79.2\%) & 576 (92.7\%)\\
 \code{airquality} & 5,496 & 4,551 (17.2\%) & 1,241 (77.4\%) & 2,874 (47.7\%) & 1,294 (76.5\%)\\
 \code{faithful} & 5,136 & 4,543 (11.5\%) & 1,339 (73.9\%) & 4,936 (3.9\%) & 1,776 (65.5\%)\\
   \hline
 All & 605,256 & 461,667 (24\%) & 138,937 (77\%) & 435,360 (28\%) & 142,134 (77\%)\\
\hline
\end{tabular}
\caption{(Top) Relative space savings of Protocol Buffers and native \proglang{R} serialization over the raw object sizes of each of the 104 data sets in the \pkg{datasets} package. Points to the left of the dashed $y=x$ line represent datasets that are more efficiently encoded with Protocol Buffers. (Bottom) Absolute space savings of three outlier datasets and the aggregate performance of all datasets.}
\label{fig:compression}
\end{figure}

>>>>

\author{Dirk Eddelbuettel\\Debian Project \And 
        Murray Stokely\\Apple, Inc. \And
        Jeroen Ooms\\University of California,\\Los Angeles}
\Plainauthor{Dirk Eddelbuettel, Murray Stokely, Jeroen Ooms}

@@

  Murray Stokely\\
  Apple, Inc.\\
  1 Infinite Loop\\
  Cupertino, CA, United States of America\\
  E-mail: \email{murray@stokely.org}\\
  URL: \url{http://www.stokely.org/}\\

@@

  Data set & \code{object.size} & \multicolumn{2}{c}{\proglang{R} serialization} &
  \multicolumn{2}{c}{\pkg{RProtoBuf} serialization} \\
  & & default & gzipped & default & gzipped \\
  \hline
 \code{crimtab} & 7,936 & 4,641 (41.5\%) & 714 (91.0\%) & 1,655 (79.1\%) & 576 (92.7\%)\\
 \code{airquality} & 5,496 & 4,551 (17.2\%) & 1,242 (77.4\%) & 2,874 (47.7\%) & 1,294 (76.4\%)\\
 \code{faithful} & 5,136 & 4,543 (11.5\%) & 1,339 (73.9\%) & 4,936 \phantom{0}(3.9\%) & 1,776 (65.4\%)\\
   \hline
 All & 609,024 & 463,833 (24\%) & 139,814 (77\%) & 436,746 (28\%) & 142,783 (77\%)\\
\hline
\end{tabular}
\caption{(Top) Relative space savings of Protocol Buffers and native \proglang{R} serialization over the raw object sizes of each of the 104 data sets in the \pkg{datasets} package. Points to the left of the dashed $y=x$ line represent datasets that are more efficiently encoded with Protocol Buffers. (Bottom) Absolute space savings of three outlier datasets and the aggregate performance of all datasets.
R version 3.3.1 was used for both the figure and the table. }
\label{fig:compression}
\end{figure}
